\begin{section}{Anonymous/Not logged in User}


    \begin{subsection}{Register.} The landing page for a not logged in user consists of several elements. One of these is a Register button. Clicking this brings the user to a registration page. This page has several text fields (name, gender, email address (optional), date of birth, preferred language, password, confirm password) and a Confirm button. If the form is filled out incorrectly (2 passwords not equal, password not according to specifications, required field empty,...) and the user clicks Confirm, he is informed of this and given the option to fix it. If it is filled out correctly and the user clicks Confirm, the registration is succesful and the user is brought to the landing page for an Independent user.\end{subsection}
	\begin{subsection}{Do unrestricted quizzes.} The landing page for a not logged in user also has a link to the unrestricted quizzes. Clicking this brings them to a list of all the unrestricted quizzes. Each quiz has a Start button. Clicking this brings them to the startpage of the quiz.\end{subsection}
    \begin{subsection}{Change preferred language (not persistent)}The landing page also has a language selection item. Selecting the preferred language changes the language of the application for the session.\end{subsection}
    \begin{subsection}{Log in}On the landing page there are also a number of fields for logging in (Bebras ID and password) and a button. If the ID-password combo is a valid one, the user is brought to the landing page for his User Role. If it isn't he is informed of this so he can fix the errors. \end{subsection}


\end{section}
\begin{section}{Independent User}

    \begin{subsection}{Change password}
		\label{indep-pass}
		On the landing page of an Independent user there is a link to a Settings page. This page has, amongst others, several fields for the purpose of changing the password (current password, new password, repeat new password). If these are filled out correctly (current password is correct, new password is repeated correctly, new password is according to specifications), the password is changed. If they aren't, then the user is informed of this.
    \end{subsection}
    \begin{subsection}{Change email address}
    	\label{indep-email}
    	The settings page also has a field and button for changing the email address. If a correctly formatted email address is put into the field, the email is changed after pressing the button. If there isn't, the user is informed of this.
    \end{subsection}
    \begin{subsection}{Change preferred language}
    The settings page has a dropdown box with the three language choices in it (Dutch, French, German). Selecting the preferred language and clicking the save button saves this preference and changes the language the page is in. This new information is persistent for the user his account.
    	\label{indep-lang}
    \end{subsection}
    \begin{subsection}{Do unrestricted quizzes}
    	\label{indep-unrest}
    	The landing page of an independent user has a link to the unrestricted quizzes page. This page has a list of all unrestricted quizzes he can do (except the ones he has already done). Each quiz has a start button which brings the user to the starting page of the quiz.
    \end{subsection}
    \begin{subsection}{View results and statistics from quizzes/contests he previously participated in}
    	\label{indep-resstat}
    	The landing page has a link to a Previous Contests/Quizzes page. This page has a list of quizzes and contests the user has completed. Next to each contest is mentioned what class he has done it with. Each quiz/contest has 2 links: one to a feedback page, one to a statistics page which shows his marks and his position in the class (if any).
    \end{subsection}
    \begin{subsection}{View the classes he has been associated with}
    The landing page has a link to a Classes page. This page has a list of all classes the user was part of in the past. Each class mentions the teacher and school.
    	\label{indep-class}
    \end{subsection}
    \begin{subsection}{Logout}
    	\label{indep-logout}
    	Every page except for quiz and contests pages has a log out button. Pressing this button logs the user out of the system and brings him to the landing page for a not logged in user.
    \end{subsection}
    
    \end{section}
    

\begin{section}{Pupil}

    \begin{subsection}{Change password}Equal to \ref{indep-pass}.\end{subsection}
    \begin{subsection}{Change email address}Equal to \ref{indep-email}.\end{subsection}
    \begin{subsection}{Change preferred language}Equal to \ref{indep-lang}.\end{subsection}
    \begin{subsection}{Do unrestricted quizzes}Equal to \ref{indep-unrest}.\end{subsection}
    \begin{subsection}{Participate in contests that have been opened for his class by the teacher (both restricted as official)}On the landing page for a Pupil, there is also a link to a contests page. This page has a list of all the contests (both official as restricted) the user can compete in. In most cases this will only be one. Each contest also has a Start button. Clicking this sends the user to the starting page of the competition.\end{subsection}
    \begin{subsection}{View results and statistics from quizzes/contests he previously participated in}Equal to \ref{indep-resstat}\end{subsection}
    \begin{subsection}{View the classes he has been associated with and his current class}Similar to \ref{indep-class}. The only difference is that he can also see which class he is currently registered in.\end{subsection}
	\begin{subsection}{Logout}Equal to \ref{indep-logout}\end{subsection}

\end{section}