\section{The teacher}

A teacher registers with the organisation by email and is given a user id and password. During
registration the teacher also informs the organization of the school(s) for which he is a teacher. If the school is unknown to the organization, the teacher also must provide some general information about the school, by email. \\
\\
A database is assigned to the organisation in which information is held of the participant schools and teachers. Also the organisation can add schools with information send by a teacher only if no information was available. \\
Like any other user he can change his password and some of his personal information (telephone numbers, email address).\\
It is the teacher's task to register pupils and assign them to classes. This can be done one by one online, or by uploading a CSV or XSLX file. It is also the teachers responsibility to register classes for which they are responsible and link them to the correct school.\\
\\
When a teacher wants a class to enter the official Bebras competition, he should open the competition, as described above, and close it afterwards. A teacher can also create, open and close local competitions. For this purpose he is also allowed to browse the restricted question sets and their feedback pages.\\
\\
After a competition is finished he can download the marks of all his pupils (also for the official competition, as long as it is also officially closed). Marks are saved in a CSV-sort of file, on a central server (see below). This file will be used to inform the teacher about the marks.\\
\\
During a competition he can monitor his pupils (whether they are logged in, how much time they have left, whether they already hit the 'finished' button, ...). This is done by the use of cookies which are send to a central server which holds information about every participant within a contest. This server can be consulted by the teacher in order to obtain information about whether pupils are logged in, how much time they have left etc. When encountering connection loss problems, information about the competition can easily be consulted.  \\
\\
He can also 'reset' a pupils account during a competition and grant him some 'grace minutes' (see above).