\begin{uc}{Independent user: change password}

    \begin{uc-mss}
    \item The user clicks on "change password".
    \item The user is taken to a page that allows him to change his password.
    \item The user types his current password.
    \item The user types in his email that he used to register himself.
    \item The user types in his/here new password.
    \item The user repeats his/here new password.
    \item The user clicks on "submit".
    \item The user is redirected back to his landing-page
    \end{uc-mss}

    \begin{uc-ext}
        \begin{uc-fail}{3}{Invalid current password}
        \item Error message: Wrong password.
        \item Return to MSS step 2.
        \item ETC
        \end{uc-fail}
        
        \begin{uc-fail}{4}{Wrong email format}
        \item Error message: wrong email format.
        \item Return to MSS step 2.
        \end{uc-fail}
        
        \begin{uc-fail}{4}{Invalid email address}
        \item Error message: provided email address is not associated with user
        \item Return to MSS step 2.
        \end{uc-fail}
        
        \begin{uc-fail}{4}{Repeated input of wrong information}
        \item Error message: Repeated input of invalid information
        \item If an email is associated with account, send email to tell the owner that 3 attempts to provide information for chanage his password have accoured.
        \item Return to MSS 1.
        \end{uc-fail}
        
        \begin{uc-fail}{6}{New provided password dont match}
        \item Error message: Newly provided passwords didnt match
        \item Return to MSS step 2.
        \end{uc-fail}
	
		\begin{uc-fail}{7}{Empty fields}
		\item Error message: There are emtpy fields.
		\item Identify the empty fields.
		\item Return to MSS step 2.
		\end{uc-fail}
    \end{uc-ext}

    \begin{uc-pre}
    \item The user is logend into the system
    \item The user has a email associated with his account
    \end{uc-pre}

    \begin{uc-post}
    \item The user password is changed
    \item The user received an email with a notice that his password is changed.
    \end{uc-post}

    \begin{uc-trig}
        The user clicked on "change password" on his landing page.
    \end{uc-trig}

\end{uc}
