\begin{uc}{Database errors}


    \begin{uc-mss}
    \item Request from DriverManager a connection.
    \item Create sqlStatement.
    \item Execute sqlStatement.
    \item Get information.
    \item Display information.
    \item Close database connection.
    \end{uc-mss}

    \begin{uc-ext}

        \begin{uc-fail}{1}{Could not connect to databse}
        \item Error messsage: Error while requesting a database Connection from the database-pool.
        \item Return to page.
        \end{uc-fail}
        
        \begin{uc-fail}{2}{Error while constructing sqlStatement}
        \item Error message: Error while constructing sqlStatement, please contact administrator
        \item Return to page.
        \end{uc-fail}
        
        \begin{uc-fail}{3}{Database connection timeoud while executing statement}
        \item While there still is a valid connection and the sqlStatement is correct, retry.
        \item If retry failed, Error message: Connection timeout. Please contact administrator.
        \item Return to page
        \end{uc-fail}
        
        \begin{uc-fail}{4}{Error while using ResultSet}
        \item Error message: Invalid ResultSet returned from database. Please contact administrator.
        \item Return to page.
        \end{uc-fail}
        
        
        \begin{uc-fail}{5}{Error while returning database resource back to system}
        \item Error message: Display generic database error
        \item Return to page.
        \end{uc-fail}
        

    \end{uc-ext}

    \begin{uc-pre}
    \item A valid senario to use the database.
    \end{uc-pre}

    \begin{uc-post}
    \item All used database resources should be release back to the system.
    \item All connections should be closed.
    \end{uc-post}

    \begin{uc-trig}
    	Valid use for database.
    \end{uc-trig}

\end{uc}
