
\begin{uc}{Contact a Human}

    \begin{uc-mss}
    \item The system shows the contact page, with a form.
    \item The user fills in his subject, selects a cathegory from a list of
        cathegories, fills in his email address (automatically filled in if the
        user is logged in) and enters his message into the field.

        The cathegories for the message are:
        \begin{itemize}
        \item Teacher application.
        \item Bug report.
        \item Help request.
        \item Other.
        \end{itemize}
    \item The system mails the message with as subject ``[<cathegory>]
        <user-subject>'' to the organizers. In case of a Bug report, it is only
        sent to the administrator. The user is redirected to the home page.
    \end{uc-mss}

    \begin{uc-ext}

        \begin{uc-fail}{2}{Field left empty}
        \item The system warns the user of his mistake. It redirects him back to
            the contact page, where the previous values are still filled in.
            \return{2}
        \end{uc-fail}

    \end{uc-ext}

    \begin{uc-pre}
    \item The user is on the home page.
    \item All organizers and administrators have a mail address set.
    \end{uc-pre}

    \begin{uc-post}
    \item A mail was sent to the organizers, with as reply-to address the
        address the user filled in.
    \item The user is back on the home page.
    \end{uc-post}

    \begin{uc-trig}
        The user clicks on the ``Contact'' link.
    \end{uc-trig}

\end{uc}

