
\begin{uc}{Reset password}

    \begin{uc-mss}
    \item The system shows the list of users he's responsible for to the user.
        (The resetting user is hereafter called ``moderator''.)
    \item The moderator searches the user in this list, selects him, and clicks
        on the reset password button. \extend{Search User}
    \item The system generates a new password for the user, stores it's hash and
        mails the original to the provided address. The moderator is redirected
        to the list of users.
    \end{uc-mss}

    \begin{uc-ext}

        \begin{uc-fail}{3}{No email address is associated with the account}
        \item The system asks the moderator to fill in the users email address
            and explains how it cannot reset a password without an address to
            send it to.
        \item The moderator leaves the page.
            \return{1}
        \end{uc-fail}

        \begin{uc-fail}{3}{No email address is associated with the account; the
            user requested a reset by mail}
        \item The system asks the moderator to fill in the users email address
            and explains how it cannot reset a password without an address to
            send it to.
        \item The moderator fills in the user's email address.
            \return{3}
        \end{uc-fail}

    \end{uc-ext}

    \begin{uc-pre}
    \item The user is logged in as teacher, organizer or administrator.
    \end{uc-pre}

    \begin{uc-post}
    \item The forgetful user is provided with a new password to login.
    \end{uc-post}

    \begin{uc-trig}
        The user goes to his class or user list.
    \end{uc-trig}

\end{uc}

